The Host Galaxies of 106 Rapidly Evolving Transients discovered by the Dark Energy Survey

### 2020-07-20 DES_RET_Hosts_replyref.tex

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
%Co-authors:
\newcommand{\phil}[1]{\color{red}#1 \color{black}}
\newcommand{\mike}[1]{\color{cyan}#1 \color{black}}
\newcommand{\replyrick}[1]{\color{magenta}#1 \color{black}}
\newcommand{\replylluis}[1]{\color{brown}#1 \color{black}}
\newcommand{\comment}[1]{\textbf{[#1]}} %comments

%define some nice astro shortcuts
\newcommand{\halpha}[0]{H$\alpha$}
\newcommand{\hbeta}[0]{H$\beta$}
\newcommand{\hgamma}[0]{H$\gamma$}
\newcommand{\hdelta}[0]{H$\delta$}
\newcommand{\hepsilon}[0]{H$\epsilon$}
\newcommand{\HII}[0]{$[\textnormal{\textsc{Hii}}]$}
\newcommand{\OII}[0]{$[\textnormal{\textsc{Oii}}]$}
\newcommand{\OI}[0]{$[\textnormal{\textsc{Oi}}]$}
\newcommand{\OIII}[0]{$[\textnormal{\textsc{Oiii}}]$}
\newcommand{\SII}[0]{$[\textnormal{\textsc{Sii}}]$}
\newcommand{\SIII}[0]{$[\textnormal{\textsc{Siii}}]$}
\newcommand{\NII}[0]{$[\textnormal{\textsc{Nii}}]$}
\newcommand{\msun}[0]{M_{\odot}}
\usepackage{etoolbox}
\makeatletter
\patchcmd\@combinedblfloats{\box\@outputbox}{\unvbox\@outputbox}{}{%
  \errmessage{\noexpand\@combinedblfloats could not be patched}%
}%
\makeatother

@@

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[RET host galaxies in DES]{The Host Galaxies of Rapidly Evolving Transients in the Dark Energy Survey}
% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[P. S. Wiseman]{
\parbox{\textwidth}{
\Large
P.~Wiseman,$^{1}$
M.~Pursiainen,$^{1}$
M.~Childress,$^{1}$
E.~Swann,$^{2}$
M.~Smith,$^{1}$
L.~Galbany,$^{3}$
C.~Lidman,$^{4}$
T.~M.~Davis,$^{5}$
C.~P.~Guti\'errez,$^{1}$
A.~M\"oller,$^{6}$
B.~P.~Thomas,$^{2}$
C.~Frohmaier,$^{2}$
R.~J.~Foley,$^{7}$
S.~R.~Hinton,$^{5}$
L.~Kelsey,$^{1}$
R.~Kessler,$^{8,9}$
G.~F.~Lewis,$^{10}$
M.~Sako,$^{11}$
D.~Scolnic,$^{12}$
M.~Sullivan,$^{1}$
M.~Vincenzi,$^{2}$
T.~M.~C.~Abbott,$^{13}$
M.~Aguena,$^{14,15}$
S.~Allam,$^{16}$
J.~Annis,$^{16}$
E.~Bertin,$^{17,18}$
S.~Bhargava,$^{19}$
D.~Brooks,$^{20}$
D.~L.~Burke,$^{21,22}$
A.~Carnero~Rosell,$^{23}$
D.~Carollo,$^{24}$
M.~Carrasco~Kind,$^{25,26}$
J.~Carretero,$^{27}$
M.~Costanzi,$^{28,29}$
L.~N.~da Costa,$^{15,30}$
H.~T.~Diehl,$^{16}$
P.~Doel,$^{20}$
S.~Everett,$^{7}$
P.~Fosalba,$^{31,32}$
J.~Frieman,$^{16,9}$
J.~Garc\'ia-Bellido,$^{33}$
E.~Gaztanaga,$^{31,32}$
K.~Glazebrook,$^{34}$
D.~Gruen,$^{35,21,22}$
R.~A.~Gruendl,$^{25,26}$
J.~Gschwend,$^{15,30}$
G.~Gutierrez,$^{16}$
D.~L.~Hollowood,$^{7}$
K.~Honscheid,$^{36,37}$
D.~J.~James,$^{38}$
K.~Kuehn,$^{39,40}$
N.~Kuropatkin,$^{16}$
M.~Lima,$^{14,15}$
M.~A.~G.~Maia,$^{15,30}$
J.~L.~Marshall,$^{41}$
P.~Martini,$^{36,42}$
F.~Menanteau,$^{25,26}$
R.~Miquel,$^{43,27}$
A.~Palmese,$^{16,9}$
F.~Paz-Chinch\'{o}n,$^{44,26}$
A.~A.~Plazas,$^{45}$
A.~K.~Romer,$^{19}$
E.~Sanchez,$^{23}$
V.~Scarpine,$^{16}$
M.~Schubnell,$^{46}$
S.~Serrano,$^{31,32}$
I.~Sevilla-Noarbe,$^{23}$
N.~E.~Sommer,$^{4}$
E.~Suchyta,$^{47}$
M.~E.~C.~Swanson,$^{26}$
G.~Tarle,$^{46}$
B.~E.~Tucker,$^{4}$
D.~L.~Tucker,$^{16}$
T.~N.~Varga,$^{48,49}$
and A.~R.~Walker$^{13}$
\begin{center} (DES Collaboration) \end{center}
}
\vspace{0.4cm}
\\
\parbox{\textwidth}{Affiliations are listed at the end of the paper}
}
% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

@@

% Abstract of the paper
\begin{abstract}
Rapidly evolving transients (RETs), also termed fast blue optical transients (FBOTs), are a distinct class of astrophysical event. They are characterised by lightcurves that decline much faster than common classes supernovae (SNe), span vast ranges in peak luminosity and can be seen to redshifts greater than 1. Their evolution on fast timescales has hindered high quality follow-up observations, and thus their origin and explosion/emission mechanism remains unexplained. In this paper we define the largest sample of RETs to date, comprising 106 objects from the Dark Energy Survey, and perform the most comprehensive analysis of RET host galaxies. Using deep-stacked photometry and emission-lines from OzDES spectroscopy, we derive stellar masses and star-formation rates (SFRs) for 49 host galaxies, and metallicities for 37. We find that RETs explode exclusively in star-forming galaxies and are thus likely associated with massive stars. Comparing RET hosts to samples of host galaxies of other explosive transients as well as field galaxies, we find that RETs prefer galaxies with high specific SFRs, indicating a link to young stellar populations, similar to stripped-envelope SNe. RET hosts appear to show a lack of chemical enrichment, their metallicities akin to long duration gamma-ray bursts and superluminous SN host galaxies. There are no clear relationships between properties of the host galaxies and the peak magnitudes or decline rates of the transients themselves.

@@

In the standard paradigm of stellar evolution, stars with a zero-age main sequence (ZAMS) mass above $8M_{\sun}$ are believed to explode as a result of a catastrophic collapse of their iron cores and are known as core-collapse supernovae (CCSNe). CCSNe can be split into observationally-determined subclasses based on their lightcurve and spectral evolution: SNe II display hydrogen features in their spectra \citep{Minkowski1941}, and are thought to occur in stars that retain a large fraction of their hydrogen envelope. Conversely, SNe Ib and Ic do not show signatures of hydrogen \citep[e.g.][]{Filippenko1997} and are thus referred to collectively as stripped-envelope SNe (SESNe), having undergone a partial removal of their outer atmospheres. The SN IIb subclass, which shows hydrogen only at early epochs that disappears after a few weeks \citep{Filippenko1988}, is also commonly grouped along with SESNe. SNe IIn display much narrower hydrogen emission lines when compared to standard SNe II \citep{Schlegel1990}. The narrow emission originates from the ejecta impacting on slow-moving circumstellar material (CSM). Since the turn of the century, observations of CCSNe, whose lightcurves are primarily powered by the radioactive decay of freshly synthesised Ni-56, have been supplemented by rarer, more exotic transient classes.

@@

 Along with observations of the transients themselves, studies of host galaxies are frequently used to make strong inferences about the progenitor stars and explosion mechanisms. CCSNe are confined almost exclusively to galaxies hosting recent or ongoing star formation, due to their origin from massive stars. There are correlations between the expected progenitor mass of different sub-classes of CCSNe and host galaxy properties. On average, SESNe reside in galaxies with higher specific star-formation rates (sSFRs; \citealt{James2006,Kelly2008}), while studies of the local environments tend to show that SESNe explode closer to \HII~regions than SNe II, indicating that the progenitors are younger and more massive than the various sub-classes of hydrogen-rich SNe II  \citep[e.g.][]{Anderson2012,Galbany2018}. More extreme events tend to occur in galaxies low in mass and high in sSFR, with both LGRBs \citep[e.g.][]{Fruchter2006,LeFloch2006,Levesque2010,Kruehler2015,Vergani2015,Perley2016b,Palmerio2019,Taggart2019} and to an even greater degree SLSNe \citep[e.g.][]{Neill2011,Lunnan2014,Leloudas2015,Angus2016,Schulze2018,Taggart2019} exhibiting this association.

@@

Recently, inspection of high-cadence, large-area survey data sets have revealed more exotic transients that are difficult to explain with conventional models. \citet{Drout2014} presented a sample of rapidly evolving transients (RETs; also termed `Fast Blue Optical Transients' - FBOTs or `Fast Evolving Luminous Transients' - FELTs) in the Pan-STARRS survey (PS1). \citet{Arcavi2016} reported three rapidly rising, highly luminous objects in the Supernova Legacy Survey (SNLS) and one in the Palomar Transient Factory (PTF), of which one (SNLS04D4ec) declines rapidly like the PS1 sample. \citet[hereafter P18]{Pursiainen2018} expanded the known number of RETs to beyond 80 with their sample from the Dark Energy Survey (DES), spanning a redshift range of $\sim 0$ to $>1$. A further sample of five objects has been discovered by the Hyper Suprime-Cam Subaru Strategic Program (SSP) Transient Survey \citep{Tampo2020}. RETs typically rise to peak brightness in less than 10 days, and decline to 10\% of their peak brightness within 30 days, much faster than typical SNe. The photometric measurements of the PS1 and DES RETs seem to be well described by expanding blackbodies, although a handful show declining photospheric radii from the first detection. Due to the rapid nature of their lightcurves and location at high-redshift, spectral coverage is sparse and signal-to-noise ratio (SNR) is low, such that there has not yet been a conclusive detection of absorption or emission features from the transients and thus the physical mechanism responsible for their rapid evolution remains unexplained.

There are a limited number of events detected in the local Universe whose properties appear consistent with the RETs seen at cosmological distances in the PS1 and DES samples, the most widely studied of which is AT2018cow \citep[e.g.][]{Prentice2018,Margutti2019,Perley2019}. The transient declined from its discovery, with constraints on the rise time of 1 day, and from X-rays through to radio wavelengths did not resemble any known SN, GRB afterglow, or kilonova (KN; \citealt{Ho2019}) . There are many diverse explanations for the power source of AT2018cow touted in the literature, including: magnetars \citep{Mohan2020}; electron capture collapse of merged white dwarfs \citep{Lyutikov2019}; a tidal disruption event (TDE) of a white dwarf \citep{Kuin2019} or of a main sequence star by an intermediate mass black hole \citep{Perley2019}; common envelope jets supernova (CEJSN; \citealt{Soker2019}); or a wind-driven transient \citep{Uno2020}.
Other nearby rapid transients include the local fast-declining SN-like transient SN2018kzr \citep{McBrien2019} which is explained by the accretion-induced collapse of a white dwarf or a white dwarf-neutron star merger, and KSN-2015K \citep{Rest2018} whose fast rise and decline is explained by the shock of an SN running into previously-expelled material.  It is currently unclear whether these transients represent the local analogues of the DES and PS1 RETs.

@@

The order of the paper is as follows: in Section \ref{sec:sample} we introduce the full DES RET sample and describe the host galaxy observations in Section \ref{sec:obs}. The analysis methods and results are described in Sections \ref{sec:measure} and \ref{sec:analysis} respectively, before a discussion (Section \ref{sec:disc}) and conclusion (Section \ref{sec:conc}).
Where applicable, we adopt a spatially flat $\Lambda$CDM cosmology with the parameters $H_0=70$ km~s$^{-1}$ Mpc$^{-1}$ and $\Omega_{\textrm{M}}=0.3$. Magnitudes are presented in the AB system \citep{Oke1983}, and values (uncertainties) are quoted at the 50\textsuperscript{th} (16\textsuperscript{th} and 84\textsuperscript{th}, i.e. $1\sigma$) percentiles of their probability density function.

@@

Figs.~\ref{fig:sfms_ssfr} and \ref{fig:sfms_ssfr_other} are similar to Figs.~\ref{fig:sfms_sfr} and \ref{fig:sfms_ssfr_other}, except that here SFR has been normalised by stellar mass, and thus shows the specific star-formation rate (sSFR), which is a more representative measure of the star-forming efficiency. It is once again clear that RET hosts lie systematically above the majority of SDSS star-forming galaxies in terms of sSFR. Normalised by mass, it is here perhaps clearer to see that RET hosts lie at higher sSFR than CCSNe hosts, but not in the extremely star-forming environments of LGRBs or SLSNe.

@@

    \label{tab:summary}
\end{table}
\section{Discussion}

\subsection{Selection Biases \label{subsec:disc_bias}}
The properties presented in Section \ref{sec:analysis} are derived from a subset of the total sample of RETs. Of 106 objects, under half (52/106) have secure host galaxy redshifts. Three of these were obtained from transient spectra, for which we are unable to disentangle the host and transient contributions, and four were obtained by programmes for which we do not have access to the spectra. Of the remaining 45, it was possible to derive a metallicity or at least a limit for 40 host galaxies, while five exceeded the redshift range for the necessary lines to fall within the wavelength coverage of AAOmega. The observed metallicity distribution could have arisen if the galaxies without redshifts (and metallicities) are systematically higher in metallicity than those for which measurements were possible. For low SNR objects, redshifts are typically obtained from only two of the strongest lines (e.g. \halpha, \hbeta, \OIII, and \OII). It is likely that the redshifts were not obtained because the galaxies are physically smaller or are at higher redshift. However, galaxies with high metallicity have weaker \OIII~lines, meaning they are less likely to have a redshift detection compared to less enriched galaxies with the same mass and redshift. Future, deeper spectral observation programmes as well as large, complete low-redshift samples are necessary to reduce this possible bias.

>>>>

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
%Co-authors:
\newcommand{\phil}[1]{\color{red}#1 \color{black}}
\newcommand{\mike}[1]{\color{cyan}#1 \color{black}}
\newcommand{\replyref}[1]{\color{magenta}#1 \color{black}}
\newcommand{\replylluis}[1]{\color{brown}#1 \color{black}}
\newcommand{\comment}[1]{\textbf{[#1]}} %comments

%define some nice astro shortcuts
\newcommand{\halpha}[0]{H$\alpha$}
\newcommand{\hbeta}[0]{H$\beta$}
\newcommand{\hgamma}[0]{H$\gamma$}
\newcommand{\hdelta}[0]{H$\delta$}
\newcommand{\hepsilon}[0]{H$\epsilon$}
\newcommand{\HII}[0]{$[\textnormal{\textsc{Hii}}]$}
\newcommand{\OII}[0]{$[\textnormal{\textsc{Oii}}]$}
\newcommand{\OI}[0]{$[\textnormal{\textsc{Oi}}]$}
\newcommand{\OIII}[0]{$[\textnormal{\textsc{Oiii}}]$}
\newcommand{\SII}[0]{$[\textnormal{\textsc{Sii}}]$}
\newcommand{\SIII}[0]{$[\textnormal{\textsc{Siii}}]$}
\newcommand{\NII}[0]{$[\textnormal{\textsc{Nii}}]$}
\newcommand{\msun}[0]{M_{\odot}}
\usepackage{etoolbox}
%\makeatletter
%\patchcmd\@combinedblfloats{\box\@outputbox}{\unvbox\@outputbox}{}{%
%  \errmessage{\noexpand\@combinedblfloats could not be %patched}%
%}%
%\makeatother

@@

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
%\title[RET host galaxies in DES]{The Host Galaxies of Rapidly Evolving Transients in the Dark Energy Survey}
\title[RET host galaxies in DES]{The Host Galaxies of 106 Rapidly Evolving Transients discovered by the Dark Energy Survey}
% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[P. S. Wiseman]{
\parbox{\textwidth}{
\Large
P.~Wiseman,$^{1}$
M.~Pursiainen,$^{1}$
M.~Childress,$^{1}$
E.~Swann,$^{2}$
M.~Smith,$^{1}$
L.~Galbany,$^{3}$
C.~Lidman,$^{4}$
T.~M.~Davis,$^{5}$
C.~P.~Guti\'errez,$^{1}$
A.~M\"oller,$^{6}$
B.~P.~Thomas,$^{2}$
C.~Frohmaier,$^{2}$
R.~J.~Foley,$^{7}$
S.~R.~Hinton,$^{5}$
L.~Kelsey,$^{1}$
R.~Kessler,$^{8,9}$
G.~F.~Lewis,$^{10}$
M.~Sako,$^{11}$
D.~Scolnic,$^{12}$
M.~Sullivan,$^{1}$
M.~Vincenzi,$^{2}$
T.~M.~C.~Abbott,$^{13}$
M.~Aguena,$^{14,15}$
S.~Allam,$^{16}$
J.~Annis,$^{16}$
E.~Bertin,$^{17,18}$
S.~Bhargava,$^{19}$
D.~Brooks,$^{20}$
D.~L.~Burke,$^{21,22}$
A.~Carnero~Rosell,$^{23}$
D.~Carollo,$^{24}$
M.~Carrasco~Kind,$^{25,26}$
J.~Carretero,$^{27}$
M.~Costanzi,$^{28,29}$
L.~N.~da Costa,$^{15,30}$
H.~T.~Diehl,$^{16}$
P.~Doel,$^{20}$
S.~Everett,$^{7}$
P.~Fosalba,$^{31,32}$
J.~Frieman,$^{16,9}$
J.~Garc\'ia-Bellido,$^{33}$
E.~Gaztanaga,$^{31,32}$
K.~Glazebrook,$^{34}$
D.~Gruen,$^{35,21,22}$
R.~A.~Gruendl,$^{25,26}$
J.~Gschwend,$^{15,30}$
G.~Gutierrez,$^{16}$
D.~L.~Hollowood,$^{7}$
K.~Honscheid,$^{36,37}$
D.~J.~James,$^{38}$
K.~Kuehn,$^{39,40}$
N.~Kuropatkin,$^{16}$
M.~Lima,$^{14,15}$
M.~A.~G.~Maia,$^{15,30}$
J.~L.~Marshall,$^{41}$
P.~Martini,$^{36,42}$
F.~Menanteau,$^{25,26}$
R.~Miquel,$^{43,27}$
A.~Palmese,$^{16,9}$
F.~Paz-Chinch\'{o}n,$^{44,26}$
A.~A.~Plazas,$^{45}$
A.~K.~Romer,$^{19}$
E.~Sanchez,$^{23}$
V.~Scarpine,$^{16}$
M.~Schubnell,$^{46}$
S.~Serrano,$^{31,32}$
I.~Sevilla-Noarbe,$^{23}$
N.~E.~Sommer,$^{4}$
E.~Suchyta,$^{47}$
M.~E.~C.~Swanson,$^{26}$
G.~Tarle,$^{46}$
B.~E.~Tucker,$^{4}$
D.~L.~Tucker,$^{16}$
T.~N.~Varga,$^{48,49}$
and A.~R.~Walker$^{13}$
\begin{center} (DES Collaboration) \end{center}
}
\vspace{0.4cm}
\\
\parbox{\textwidth}{Affiliations are listed at the end of the paper}
}
% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

@@

% Abstract of the paper
\begin{abstract}
Rapidly evolving transients (RETs), also termed fast blue optical transients (FBOTs), are a recently-discovered group of astrophysical events that display rapid luminosity evolution. RETs typically rise to peak in less than 10 days and fade within 30, a timescale unlikely to be compatible with the decay of Nickel-56 that drives conventional SNe. Their peak luminosity spans a range of $-15 <M_g<-22.5$, with some events observed at redshifts greater than 1. Their evolution on fast timescales has hindered high quality follow-up observations, and thus their origin and explosion/emission mechanism remains unexplained. In this paper we define the largest sample of RETs to date, comprising 106 objects from the Dark Energy Survey, and perform the most comprehensive analysis of RET host galaxies. Using deep-stacked photometry and emission-lines from OzDES spectroscopy, we derive stellar masses and star-formation rates (SFRs) for 49 host galaxies, and metallicities ([O/H]) for 37. We find that RETs explode exclusively in star-forming galaxies and are thus likely associated with massive stars. Comparing RET hosts to samples of host galaxies of other explosive transients as well as field galaxies, we find that RETs prefer galaxies with high specific SFRs ($\langle\log \left(\mathrm{sSFR}\right)\rangle \sim -9.6$ ), indicating a link to young stellar populations, similar to stripped-envelope SNe. RET hosts appear to show a lack of chemical enrichment, their metallicities akin to long duration gamma-ray bursts and superluminous SN host galaxies $\langle12+\log\left(\mathrm{O/H}\right) \rangle \sim 9.4$. There are no clear relationships between properties of the host galaxies and the peak magnitudes or decline rates of the transients themselves.

@@

In the standard paradigm of stellar evolution, stars with a zero-age main sequence (ZAMS) mass above $8M_{\sun}$ are believed to explode as a result of a catastrophic collapse of their iron cores and are known as core-collapse supernovae (CCSNe). CCSNe can be split into observationally-determined subclasses based on their lightcurve and spectral evolution: SNe II display hydrogen features in their spectra \citep{Minkowski1941}, and are thought to occur in stars that retain a large fraction of their hydrogen envelope. Conversely, SNe Ib and Ic do not show signatures of hydrogen \citep[e.g.][]{Filippenko1997} and are thus referred to collectively as stripped-envelope SNe (SESNe), having undergone a partial removal of their outer atmospheres. The SN IIb subclass, which shows hydrogen only at early epochs that disappears after a few weeks \citep{Filippenko1988}, is also commonly grouped along with SESNe. SNe IIn display much narrower hydrogen emission lines when compared to standard SNe II \citep{Schlegel1990}. The narrow emission originates from the ejecta impacting on slow-moving circumstellar material (CSM). Since the turn of the century, observations of CCSNe, whose lightcurves are \replyref{thought to be} primarily powered by the radioactive decay of freshly synthesised Ni-56, have been supplemented by rarer, more exotic transient classes.

@@

 Along with observations of the transients themselves, studies of host galaxies are frequently used to make strong inferences about the progenitor stars and explosion mechanisms. CCSNe are confined almost exclusively to galaxies hosting recent or ongoing star formation, due to their origin from massive stars. There are correlations between the expected progenitor mass of different sub-classes of CCSNe and host galaxy properties. On average, SESNe reside in galaxies with higher specific star-formation rates (sSFRs; \citealt{James2006,Kelly2008}) \replyref{than SNe II}, while studies of the local environments tend to show that SESNe explode closer to \HII~regions than SNe II, indicating that the progenitors are younger and more massive than the various sub-classes of hydrogen-rich SNe II  \citep[e.g.][]{Anderson2012,Galbany2018}. More extreme events tend to occur in galaxies low in mass \replyref{($\leq10^{10} M_{\odot}$) and high in sSFR ($\geq 10^{-9.5}$ yr$^{-1}$)}, with both LGRBs \citep[e.g.][]{Fruchter2006,LeFloch2006,Levesque2010,Kruehler2015,Vergani2015,Perley2016b,Palmerio2019,Taggart2019} and to an even greater degree SLSNe \citep[e.g.][]{Neill2011,Lunnan2014,Leloudas2015,Angus2016,Schulze2018,Taggart2019} exhibiting this association.

@@

Recently, inspection of high-cadence, large-area survey data sets have revealed more exotic transients that are difficult to explain with conventional models. \citet{Drout2014} presented a sample of rapidly evolving transients (RETs; also termed `Fast Blue Optical Transients' - FBOTs or `Fast Evolving Luminous Transients' - FELTs) in the Pan-STARRS survey (PS1). \citet{Arcavi2016} reported three rapidly rising, highly luminous objects in the Supernova Legacy Survey (SNLS) and one in the Palomar Transient Factory (PTF), of which one (SNLS04D4ec) declines rapidly. \citet[hereafter P18]{Pursiainen2018} expanded the known number of RETs to beyond 80 with their sample from the Dark Energy Survey (DES), spanning a redshift range of $\sim 0$ to $>1$. A further sample of five objects has been discovered by the Hyper Suprime-Cam Subaru Strategic Program (SSP) Transient Survey \citep{Tampo2020}. \replyref{Although the search and selection criteria vary between the above samples, the objects} typically rise to peak brightness in less than 10 days, and decline to 10\% of their peak brightness within 30 days, much faster than typical SNe. The photometric measurements of the PS1 and DES RETs seem to be well described by expanding blackbodies, although a handful show declining photospheric radii from the first detection. Due to the rapid nature of their lightcurves and location at high-redshift, spectral coverage is sparse and signal-to-noise ratio (SNR) is low, such that there has not yet been a conclusive detection of absorption or emission features from the transients and thus the physical mechanism responsible for their rapid evolution remains unexplained.

There are a limited number of events detected in the local Universe whose properties appear consistent with the RETs seen at cosmological distances in the PS1 and DES samples, the most widely studied of which is AT2018cow \citep[e.g.][]{Prentice2018,Margutti2019,Perley2019}. The transient declined from its discovery, with constraints on the rise time of 1 day, and from X-rays through to radio wavelengths did not resemble any known SN, GRB afterglow, or kilonova (KN; \citealt{Ho2019}) . There are many diverse explanations for the power source of AT2018cow \replyref{proposed} in the literature, including: \replyref{engine-driven stellar explosions \citep{Ho2019,Margutti2019,Mohan2020}}; electron capture collapse of merged white dwarfs \citep{Lyutikov2019}; a tidal disruption event (TDE) of a white dwarf \citep{Kuin2019} or of a main sequence star by an intermediate mass black hole \citep{Perley2019}; common envelope jets supernova (CEJSN; \citealt{Soker2019}); or a wind-driven transient \citep{Piro2020,Uno2020}.
Other nearby rapid transients \replyref{that would pass the DES search criteria} include the local fast-declining SN-like transient SN2018kzr \citep{McBrien2019} which is explained by the accretion-induced collapse of a white dwarf or a white dwarf-neutron star merger, KSN-2015K \citep{Rest2018} whose fast rise and decline is explained by the shock of an SN running into previously-expelled material, \replyref{SN2018gep \citep{Ho2019a} which is a rapidly-declining, nearby SN Ic-BL, and the H-rich, relativistic CSS161010 \citep{Coppejans2020}. At higher redshift there is one RET -- ZTF18abvkwla \citep{Ho2020}.}

@@

The order of the paper is as follows: in Section \ref{sec:sample} we introduce the full DES RET sample and describe the host galaxy observations in Section \ref{sec:obs}. The analysis methods and results are described in Sections \ref{sec:measure} and \ref{sec:analysis} respectively, before a discussion (Section \ref{sec:discussion}) and conclusion (Section \ref{sec:conc}).
Where applicable, we adopt a spatially flat $\Lambda$CDM cosmology with the parameters $H_0=70$ km~s$^{-1}$ Mpc$^{-1}$ and $\Omega_{\textrm{M}}=0.3$. Magnitudes are presented in the AB system \citep{Oke1983}, and values (uncertainties) are quoted at the 50\textsuperscript{th} (16\textsuperscript{th} and 84\textsuperscript{th}, i.e. $1\sigma$) percentiles of their probability density function.

@@

Figs.~\ref{fig:sfms_ssfr} and \ref{fig:sfms_ssfr_other} are similar to Figs.~\ref{fig:sfms_sfr} and \ref{fig:sfms_sfr_other}, except that here SFR has been normalised by stellar mass, and thus shows the specific star-formation rate (sSFR), which is a more representative measure of the star-forming efficiency. It is once again clear that RET hosts lie systematically above the majority of SDSS star-forming galaxies in terms of sSFR. Normalised by mass, it is here perhaps clearer to see that RET hosts lie at higher sSFR than CCSNe hosts, but not in the extremely star-forming environments of LGRBs or SLSNe.

@@

    \label{tab:summary}
\end{table}

\section{Discussion }
\label{sec:discussion}
\subsection{Selection Biases \label{subsec:disc_bias}}
The properties presented in Section \ref{sec:analysis} are derived from a subset of the total sample of RETs. Of 106 objects, under half (52/106) have secure host galaxy redshifts. Three of these were obtained from transient spectra, for which we are unable to disentangle the host and transient contributions, and four were obtained by programmes for which we do not have access to the spectra. Of the remaining 45, it was possible to derive a metallicity or at least a limit for 40 host galaxies, while five exceeded the redshift range for the necessary lines to fall within the wavelength coverage of AAOmega. The observed metallicity distribution could have arisen if the galaxies without redshifts (and metallicities) are systematically higher in metallicity than those for which measurements were possible. For low SNR objects, redshifts are typically obtained from only two of the strongest lines (e.g. \halpha, \hbeta, \OIII, and \OII). It is likely that the redshifts were not obtained because the galaxies are physically smaller or are at higher redshift. However, galaxies with high metallicity have weaker \OIII~lines, meaning they are less likely to have a redshift detection compared to less enriched galaxies with the same mass and redshift. Future, deeper spectral observation programmes as well as large, complete low-redshift samples are necessary to reduce this possible bias.
